Long-form recording of infant body position in the home using wearable inertial sensors

### 2023-06-16 manuscript.Rmd
group_split_sensor_reduce

floatsintext      : no
linenumbers       : no
draft             : no
mask              : no
figurelist        : no
tablelist         : no
footnotelist      : no
csl               : apa.csl
classoption       : "man"
output            : papaja::apa6_pdf
header-includes:
  - \raggedbottom
editor_options: 
  chunk_output_type: console
---

>>>>

floatsintext      : no
linenumbers       : no
draft             : no
mask              : no
figurelist        : no
tablelist         : no
footnotelist      : no
biblio-style      : "apa"
classoption       : "man"
output:
  papaja::apa6_pdf:
    citation_package: biblatex
header-includes:
  - \raggedbottom
editor_options: 
  chunk_output_type: console
---
